---
title: "Excel Benchmark Index Top 2"
author: "Zain"
date: "2025-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# Load required libraries
library(dplyr)
library(tidyr)
library(openxlsx)

```

```{r}
# Function to create the Excel workbook
create_benchmark_excel <- function(kpi_files, output_file = "KPI_Benchmarks.xlsx") {
  # Create a list to store data from each KPI
  all_kpi_data <- list()
  
  # Process each KPI file
  for (i in seq_along(kpi_files)) {
    file_path <- kpi_files[i]
    
    # Extract KPI name from the file path
    kpi_name <- gsub("kpi_", "", gsub(".RData", "", basename(file_path)))
    
    cat("Processing", kpi_name, "data...\n")
    
    # Process the file
    kpi_data <- process_kpi_file(file_path, kpi_name)
    
    if (!is.null(kpi_data)) {
      # Count missing values
      missing_count <- sum(is.na(kpi_data$Benchmark))
      if (missing_count > 0) {
        cat("  Warning:", missing_count, "out of", nrow(kpi_data), 
            "benchmark values are missing for", kpi_name, "\n")
      }
      
      # Check for extreme values
      if (any(kpi_data$Benchmark > 1, na.rm = TRUE)) {
        cat("  Warning: Some benchmark values are > 1 for", kpi_name, 
            "- max value:", max(kpi_data$Benchmark, na.rm = TRUE), "\n")
      }
      
      all_kpi_data[[kpi_name]] <- kpi_data
      cat("  Processed", nrow(kpi_data), "benchmark values for", kpi_name, "\n")
    } else {
      cat("  No data processed for", kpi_name, "\n")
    }
  }
  
  # Combine all KPI data
  if (length(all_kpi_data) > 0) {
    master_data <- bind_rows(all_kpi_data)
    cat("\nCombined", nrow(master_data), "total benchmark values\n")
    
    # Check for missing values in the combined data
    missing_count <- sum(is.na(master_data$Benchmark))
    if (missing_count > 0) {
      cat("Warning:", missing_count, "out of", nrow(master_data), 
          "total benchmark values are missing\n")
    }
  } else {
    stop("No data could be processed from the KPI files")
  }
  
  # Create a pivot table for each KPI
  kpi_pivot_tables <- list()
  
  for (kpi in unique(master_data$KPI)) {
    kpi_data <- master_data %>% filter(KPI == kpi)
    
    pivot_data <- kpi_data %>%
      # Create a combination column for content and media type
      mutate(ContentMedia = paste(MediaType, ContentType, sep = ", ")) %>%
      # Select only the columns we need for pivoting
      select(Market, Audience, ContentMedia, Benchmark) %>%
      # Pivot to the desired format
      pivot_wider(
        id_cols = c(Market, Audience),
        names_from = ContentMedia,
        values_from = Benchmark
      )
    
    kpi_pivot_tables[[kpi]] <- pivot_data
  }
  
  # Create a combined table with all data in a format ready for filtering
  filter_table <- master_data %>%
    select(KPI, Market, Audience, ContentType, MediaType, Benchmark)
  
  # Create the Excel workbook
  wb <- createWorkbook()
  
  # Add a main data sheet for filtering
  addWorksheet(wb, "All Benchmarks")
  writeData(wb, "All Benchmarks", filter_table, startRow = 1, startCol = 1)
  addFilter(wb, "All Benchmarks", row = 1, cols = 1:ncol(filter_table))
  
  # Format the All Benchmarks sheet
  headerStyle <- createStyle(
    textDecoration = "bold",
    halign = "center",
    fgFill = "#4F81BD",
    fontColour = "white",
    border = "bottom"
  )
  
  addStyle(wb, "All Benchmarks", headerStyle, rows = 1, cols = 1:ncol(filter_table))
  
  # Format benchmark as percentage with proper decimals
  pctStyle <- createStyle(numFmt = "0.0%")
  benchmark_col <- which(names(filter_table) == "Benchmark")
  addStyle(wb, "All Benchmarks", pctStyle, rows = 2:(nrow(filter_table)+1), 
           cols = benchmark_col, gridExpand = TRUE)
  
  # Add individual KPI sheets for the example table format
  for (kpi in names(kpi_pivot_tables)) {
    # Get the pivot table for this KPI
    pivot_data <- kpi_pivot_tables[[kpi]]
    
    # Add a worksheet
    addWorksheet(wb, kpi)
    
    # Write the data
    writeData(wb, kpi, pivot_data, startRow = 1, startCol = 1)
    
    # Add filters
    addFilter(wb, kpi, row = 1, cols = 1:2)  # Filter by Market and Audience
    
    # Format headers
    addStyle(wb, kpi, headerStyle, rows = 1, cols = 1:ncol(pivot_data))
    
    # Format all benchmark values as percentages
    for (col in 3:ncol(pivot_data)) {
      addStyle(wb, kpi, pctStyle, rows = 2:(nrow(pivot_data)+1), 
               cols = col, gridExpand = TRUE)
    }
    
    # Auto-adjust column widths
    setColWidths(wb, kpi, cols = 1:ncol(pivot_data), widths = "auto")
  }
  
  # Add an instructions sheet
  addWorksheet(wb, "Instructions")
  writeData(wb, "Instructions", data.frame(
    Instructions = c(
      "This workbook contains benchmark values for multiple KPIs across different markets, audiences, content types, and media types.",
      "",
      "There are two ways to use this workbook:",
      "",
      "1. 'All Benchmarks' tab: Use this tab to filter and sort benchmarks by any combination of KPI, Market, Audience, Content Type, and Media Type.",
      "",
      "2. Individual KPI tabs: Each KPI has its own tab with a pivot-table style layout showing benchmarks for all combinations of content and media types.",
      "",
      "Example of how to read the data:",
      "Market: US, Audience: POSAI, KPI: Trust, Content Type: GF Content, Media Type: Videos = XX% (benchmark value)",
      "",
      "You can use this to determine if content is:",
      "- Baseline: Within ±Y% of the benchmark",
      "- Overperforming: Above the benchmark by Y%",
      "- Underperforming: Below the benchmark by Y%"
    )
  ))
  
  # Set column width for instructions
  setColWidths(wb, "Instructions", cols = 1, widths = 120)
  
  # Save the workbook
  saveWorkbook(wb, output_file, overwrite = TRUE)
  cat("\nExcel workbook created:", output_file, "\n")
}

```

```{r}
process_kpi_file <- function(file_path, kpi_name) {
  # Create a temporary environment to load the data
  temp_env <- new.env()
  
  # Load the file
  cat("Loading file:", file_path, "\n")
  load(file_path, envir = temp_env)
  
  # Get all objects in the loaded environment
  all_objects <- ls(envir = temp_env)
  cat("Found", length(all_objects), "objects in", file_path, "\n")
  
  # Initialize a list to store processed data frames
  processed_dfs <- list()
  successful_count <- 0
  
  # Process each data frame
  for (obj_name in all_objects) {
    tryCatch({
      # Get the data frame
      df <- get(obj_name, envir = temp_env)
      
      # Skip if not a data frame or has no rows
      if (!is.data.frame(df) || nrow(df) == 0) {
        next
      }
      
      # Check if df has required columns - now checking for "Percentage" only
      if (!"Percentage" %in% names(df)) {
        next
      }
      
      # Extract information from the data frame name
      name_parts <- strsplit(obj_name, "_")[[1]]
      
      # Extract market and audience - adjusted based on your name format
      if (length(name_parts) >= 3) {
        market <- name_parts[1]
        audience <- name_parts[2]
      } else {
        next
      }
      
      # Determine content_type and media_type based on the name pattern
      if (grepl("gates", obj_name)) {
        content_type <- "GF Content"
      } else {
        content_type <- "All Content"
      }
      
      # Extract media type
      if (grepl("videos", obj_name)) {
        media_type <- "Videos"
      } else if (grepl("articles", obj_name)) {
        media_type <- "Articles"
      } else if (grepl("static", obj_name)) {
        media_type <- "Static Social"
      } else {
        media_type <- "All Media"
      }
      
      # Get the percentage value - since each df has only one row, just take the first value
      percentage_value <- df$Percentage[1]
      
      # Convert to decimal if needed
      benchmark <- NA
      if (!is.na(percentage_value)) {
        if (percentage_value > 100) {
          benchmark <- percentage_value / 100
        } else if (percentage_value <= 1) {
          benchmark <- percentage_value
        } else {
          benchmark <- percentage_value / 100
        }
      } else {
        next
      }
      
      # Create row for the benchmark table
      benchmark_row <- data.frame(
        KPI = kpi_name,
        Market = toupper(market),
        Audience = audience,
        ContentType = content_type,
        MediaType = media_type,
        Benchmark = benchmark,
        # Use Source for TotalCount if available, otherwise use 0
        TotalCount = ifelse("Source" %in% names(df), as.numeric(df$Source[1]), 0)
      )
      
      # Add to our list
      processed_dfs[[obj_name]] <- benchmark_row
      successful_count <- successful_count + 1
      
      # Print progress periodically
      if (successful_count %% 20 == 0) {
        cat("Processed", successful_count, "data frames so far for", kpi_name, "\n")
      }
      
    }, error = function(e) {
      cat("Error processing", obj_name, ":", conditionMessage(e), "\n")
    })
  }
  
  # Combine all processed data frames
  if (length(processed_dfs) > 0) {
    combined_df <- bind_rows(processed_dfs)
    cat("Successfully processed", length(processed_dfs), "out of", length(all_objects), 
        "objects for", kpi_name, "\n")
    return(combined_df)
  } else {
    cat("WARNING: No data frames could be processed for", kpi_name, "\n")
    return(NULL)
  }
}
```

```{r}

# Define the KPI files to process
kpi_files <- c(
  "summary_data/Index/kpi_issue.RData",
  "summary_data/Index/kpi_trust.RData",
  "summary_data/Index/kpi_inspiration.RData",
  "summary_data/Index/kpi_brand.RData",
  "summary_data/Index/kpi_optimistic.RData"
)

# Verify files exist
file.exists(kpi_files)

# Create the Excel workbook
create_benchmark_excel(kpi_files, "KPI_Benchmarks_Index_Top2.xlsx")