---
title: "kpi"
author: "Zain"
date: "2025-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(here)

```

```{r}

 kpi <- read.csv(here("data", "kpi_var.csv"))
```

```{r}


## US 

us_trust_all_content_all_media <- kpi %>%
  select(trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>% 
  filter(market== "us")

us_trust_gates_content_all_media <- kpi %>%
  select(trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us", gates_compare_other ==1)

us_trust_all_content_videos <- kpi %>%
  select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us",  content_type %in% c("youtube", "shorts"))

us_trust_gates_content_videos <-  kpi %>%
  select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us", gates_compare_other == 1,  content_type %in% c("youtube", "shorts"))

us_trust_all_content_articles <- kpi %>%
  select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us", content_type == "article")

us_trust_gates_content_articles <- kpi %>%
  select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us", gates_compare_other == 1,  content_type == "article")

us_trust_all_content_static <- kpi %>%
select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us",  content_type %in% c("threads", "tweet", "instagram", "facebook"))
         

us_trust_gates_content_static <- kpi %>%
select (trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
  filter(market == "us", gates_compare_other == 1, content_type %in% c("threads", "tweet", "instagram", "facebook"))
         

  
```

```{r}

# Create a function to generate all dataframes for a specific country
create_trust_dfs <- function(data, country_code) {
  # Create a base name for the dataframes
  base_name <- paste0(country_code, "_trust")
  
  # Define the content type groups
  content_groups <- list(
    all_media = NULL,  # No additional filtering
    videos = c("youtube", "shorts"),
    articles = "article",
    static = c("threads", "tweet", "instagram", "facebook")
  )
  
  # Create all 8 dataframes in one go
  result_dfs <- list()
  
  for (group_name in names(content_groups)) {
    content_types <- content_groups[[group_name]]
    
    # For all content (no gates filter)
    df_name_all <- paste0(base_name, "_all_content_", group_name)
    base_filter <- data %>%
      select(trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
      filter(market == country_code)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_all]] <- base_filter
    }
    
    # For gates content
    df_name_gates <- paste0(base_name, "_gates_content_", group_name)
    base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_gates]] <- base_filter_gates
    }
  }
  
  # Return all dataframes in a list
  return(result_dfs)
}

# Create all dataframes for each country
countries <- c("us", "uk", "rsa", "in")
all_dfs <- list()

for (country in countries) {
  country_dfs <- create_trust_dfs(kpi, country)  # Using your kpi dataframe here
  all_dfs <- c(all_dfs, country_dfs)
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)

