---
title: "excel_export"
author: "Zain"
date: "2025-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}


install.packages(c("tidyverse", "openxlsx"))


```

```{r}
# Function to save only data frames ending with "_summary"
save_only_summary_dfs <- function(kpi_name, output_path = "summary_data") {
  # Ensure output directory exists
  dir.create(output_path, showWarnings = FALSE)
  
  # Find all objects in the global environment
  all_objects <- ls(envir = .GlobalEnv)
  
  # Find objects that end with "_summary" 
  summary_objects <- all_objects[grepl("_summary$", all_objects)]
  
  # Filter for objects related to the specified KPI (if kpi_name is not NULL)
  if (!is.null(kpi_name) && kpi_name != "") {
    kpi_summary_objects <- summary_objects[grepl(kpi_name, summary_objects, ignore.case = TRUE)]
  } else {
    kpi_summary_objects <- summary_objects
  }
  
  # Further filter to ensure they are data frames
  kpi_summary_dfs <- kpi_summary_objects[sapply(kpi_summary_objects, function(x) {
    is.data.frame(get(x, envir = .GlobalEnv))
  })]
  
  # Check if we found any matching data frames
  if (length(kpi_summary_dfs) > 0) {
    # Construct filename
    if (!is.null(kpi_name) && kpi_name != "") {
      filename <- file.path(output_path, paste0("kpi_", kpi_name, ".RData"))
    } else {
      filename <- file.path(output_path, "all_summary_dfs.RData")
    }
    
    # Save the data frames
    save(list = kpi_summary_dfs, file = filename)
    
    cat("Saved", length(kpi_summary_dfs), "summary data frames to", filename, "\n")
    cat("Sample of saved data frames:\n")
    print(head(kpi_summary_dfs, 10))
    
    return(TRUE)
  } else {
    cat("No summary data frames found", 
        if(!is.null(kpi_name) && kpi_name != "") paste("for KPI:", kpi_name) else "", 
        "\n")
    return(FALSE)
  }
}

# Example usage:
# To save all summary data frames for the issue KPI:
save_only_summary_dfs("brand")

# To save all summary data frames for the trust KPI:
# save_only_summary_dfs("trust")

# To save ALL summary data frames (across all KPIs):
# save_only_summary_dfs("")

```

```{r}

load("summary_data/kpi_issue.RData")
load("summary_data/kpi_trust.RData")
load("summary_data/kpi_inspiration.RData")
load("summary_data/kpi_brand.RData")












```{r} 

# First, check what's actually in your environment
all_objects <- ls(envir = .GlobalEnv)

# Print the total number of objects
cat("Total number of objects in environment:", length(all_objects), "\n")

# Look for data frames
df_objects <- all_objects[sapply(all_objects, function(x) is.data.frame(get(x)))]
cat("Total number of data frames:", length(df_objects), "\n")

# Print a sample of data frame names
if (length(df_objects) > 0) {
  cat("Sample of data frame names:\n")
  print(head(df_objects, 10))
} else {
  cat("No data frames found in environment\n")
}

# Look for objects with "summary" in their name
summary_objects <- all_objects[grepl("summary", all_objects, ignore.case = TRUE)]
cat("\nObjects with 'summary' in name:", length(summary_objects), "\n")
if (length(summary_objects) > 0) {
  cat("Sample of 'summary' objects:\n")
  print(head(summary_objects, 10))
}

# Look for objects with "issue" in their name
issue_objects <- all_objects[grepl("issue", all_objects, ignore.case = TRUE)]
cat("\nObjects with 'issue' in name:", length(issue_objects), "\n")
if (length(issue_objects) > 0) {
  cat("Sample of 'issue' objects:\n")
  print(head(issue_objects, 10))
}

# Try other possible patterns - "trust" or "kpi"
trust_objects <- all_objects[grepl("trust", all_objects, ignore.case = TRUE)]
cat("\nObjects with 'trust' in name:", length(trust_objects), "\n")
if (length(trust_objects) > 0) {
  cat("Sample of 'trust' objects:\n")
  print(head(trust_objects, 10))
}

kpi_objects <- all_objects[grepl("kpi", all_objects, ignore.case = TRUE)]
cat("\nObjects with 'kpi' in name:", length(kpi_objects), "\n")
if (length(kpi_objects) > 0) {
  cat("Sample of 'kpi' objects:\n")
  print(head(kpi_objects, 10))
}

# Create the directory for saving files
dir.create("summary_data", showWarnings = FALSE)
cat("\nCreated directory:", file.path(getwd(), "summary_data"), "\n")


```

```{r}
# Ensure the summary_data directory exists
dir.create("summary_data", showWarnings = FALSE)

# Find all objects with both "issue" and "summary" in their names
all_objects <- ls(envir = .GlobalEnv)
issue_summary_objects <- all_objects[grepl("issue", all_objects, ignore.case = TRUE) & 
                                    grepl("summary", all_objects, ignore.case = TRUE)]

# Check how many we found
cat("Found", length(issue_summary_objects), "objects with both 'issue' and 'summary' in their names\n")

# If we found very few or none, let's check for a different pattern
if (length(issue_summary_objects) < 10) {
  # Try to find objects ending with "_summary" that might be related to the issue KPI
  summary_objects <- all_objects[grepl("_summary$", all_objects)]
  cat("Found", length(summary_objects), "objects ending with '_summary'\n")
  
  # Print some examples
  if (length(summary_objects) > 0) {
    cat("Examples of objects ending with '_summary':\n")
    print(head(summary_objects, 10))
  }
  
  # Ask user to confirm which pattern to use
  cat("\nBased on the object names, we need to determine which summary objects to save.\n")
  cat("Please examine the names and decide how to identify your issue KPI summary data frames.\n")
}

# Filter for data frames only
issue_summary_dfs <- issue_summary_objects[sapply(issue_summary_objects, function(x) {
  is.data.frame(get(x, envir = .GlobalEnv))
})]

cat("Found", length(issue_summary_dfs), "data frames with both 'issue' and 'summary' in their names\n")

# If we have data frames to save, save them
if (length(issue_summary_dfs) > 0) {
  # Print example names
  cat("Examples of data frames that will be saved:\n")
  print(head(issue_summary_dfs, 10))
  
  # Save to RData file
  save(list = issue_summary_dfs, file = "summary_data/kpi_issue.RData")
  cat("Saved", length(issue_summary_dfs), "data frames to summary_data/kpi_issue.RData\n")
} else {
  cat("No matching data frames found to save.\n")
  
  # Let's look at some of the objects to determine what to save
  # Check a few of the summary objects to see if they're data frames
  if (exists("summary_objects") && length(summary_objects) > 0) {
    # Get 5 random summary objects
    samples <- sample(summary_objects, min(5, length(summary_objects)))
    
    cat("\nChecking sample summary objects:\n")
    for (obj_name in samples) {
      obj <- get(obj_name, envir = .GlobalEnv)
      cat(obj_name, "- Class:", class(obj), "\n")
      if (is.data.frame(obj)) {
        cat("  Is a data frame with", nrow(obj), "rows and", ncol(obj), "columns\n")
        cat("  Column names:", paste(names(obj), collapse=", "), "\n\n")
      } else {
        cat("  Not a data frame\n\n")
      }
    }
  }
}

# Alternative approach: Create a function to manually save a set of data frames
save_selected_dfs <- function(pattern, output_file) {
  # Find data frames matching the pattern
  all_objects <- ls(envir = .GlobalEnv)
  matching_objects <- all_objects[grepl(pattern, all_objects, ignore.case = TRUE)]
  
  matching_dfs <- matching_objects[sapply(matching_objects, function(x) {
    is.data.frame(get(x, envir = .GlobalEnv))
  })]
  
  # Save if any found
  if (length(matching_dfs) > 0) {
    save(list = matching_dfs, file = output_file)
    cat("Saved", length(matching_dfs), "data frames to", output_file, "\n")
    return(TRUE)
  } else {
    cat("No matching data frames found for pattern:", pattern, "\n")
    return(FALSE)
  }
}

# Example usage of the function (commented out)
# To save all data frames with "issue" in their name:
# save_selected_dfs("issue", "summary_data/kpi_issue.RData")


load("summary_data/kpi_issue.RData")










```{r}

# Create the directory if it doesn't exist
#dir.create("summary_data", showWarnings = FALSE)

# Find all data frames in the global environment that contain both "issue" and "summary"
all_objects <- ls(envir = .GlobalEnv)
issue_summary_df_names <- all_objects[grepl("issue", all_objects, ignore.case = TRUE) & 
                                     grepl("summary", all_objects, ignore.case = TRUE)]

# Print how many we found
cat("Found", length(issue_summary_df_names), "issue summary data frames\n")

# Display the first few data frame names (if any found)
if (length(issue_summary_df_names) > 0) {
  cat("Example data frame names:\n")
  print(head(issue_summary_df_names, 5))
} else {
  cat("No issue summary data frames found\n")
}

# Save these data frames to an RData file in the summary_data folder
if (length(issue_summary_df_names) > 0) {
  # First approach: save all data frames in one file
  save(list = issue_summary_df_names, 
       file = "summary_data/kpi_issue.RData")
  
  cat("Saved", length(issue_summary_df_names), 
      "issue summary data frames to summary_data/kpi_issue.RData\n")
}

# Alternatively, if you want to verify which data frames are being saved:
# Uncomment this section to see more details about what's being saved
#
# for (name in issue_summary_df_names) {
#   df <- get(name)
#   cat("Data frame:", name, "- Dimensions:", nrow(df), "rows x", ncol(df), "columns\n")
# }
























```{r}

kpi_files <- c(
  "path/to/kpi_trust.RData",
  "path/to/kpi_salience.RData",
  "path/to/kpi_action.RData",
  "path/to/kpi_optimism.RData", 
  "path/to/kpi_brand.RData",
  "path/to/kpi_inspiration.RData"
)

library(tidyverse)

# Function to extract all summary data frames from a KPI file
extract_summary_frames <- function(kpi_file) {
  # Create a new environment to avoid cluttering global environment
  temp_env <- new.env()
  
  # Load the file into the temporary environment
  load(kpi_file, envir = temp_env)
  
  # Extract KPI name from the file name
  kpi_name <- gsub("kpi_", "", gsub(".RData", "", basename(kpi_file)))
  
  # Get all summary data frames in the environment
  all_objects <- ls(envir = temp_env)
  summary_df_names <- all_objects[grepl("_summary$", all_objects)]
  
  # Create a list to store all data frames
  summary_dfs <- list()
  
  # Process each summary data frame
  for (df_name in summary_df_names) {
    # Get the data frame
    df <- get(df_name, envir = temp_env)
    
    # Add KPI column
    df$KPI <- kpi_name
    
    # Add source name
    df$SourceName <- df_name
    
    # Add to list
    summary_dfs[[df_name]] <- df
  }
  
  # Combine all data frames from this file
  if (length(summary_dfs) > 0) {
    combined_df <- bind_rows(summary_dfs)
    return(combined_df)
  } else {
    return(NULL)
  }
}

# List of KPI file paths - update these to your actual file paths
kpi_files <- c(
  "path/to/kpi_trust.RData",
  "path/to/kpi_salience.RData",
  "path/to/kpi_action.RData",
  "path/to/kpi_optimism.RData", 
  "path/to/kpi_brand.RData",
  "path/to/kpi_inspiration.RData"
)

# Process each KPI file and collect results
all_kpi_data <- list()
for (kpi_file in kpi_files) {
  cat("Processing", kpi_file, "...\n")
  
  # Try to process the file
  tryCatch({
    kpi_data <- extract_summary_frames(kpi_file)
    if (!is.null(kpi_data)) {
      all_kpi_data[[basename(kpi_file)]] <- kpi_data
      cat("  Found", nrow(kpi_data), "rows from", kpi_file, "\n")
    } else {
      cat("  No summary data frames found in", kpi_file, "\n")
    }
  }, error = function(e) {
    cat("  Error processing", kpi_file, ":", e$message, "\n")
  })
}

# Combine all KPI data into one master data frame
master_data <- bind_rows(all_kpi_data)

# Print summary of the combined data
cat("\nMaster data frame created with", nrow(master_data), "rows and", ncol(master_data), "columns\n")
cat("KPIs included:", paste(unique(master_data$KPI), collapse = ", "), "\n")

# Save the combined data to a RData file
save(master_data, file = "all_kpi_summary_data.RData")
cat("Combined data saved to 'all_kpi_summary_data.RData'\n")

# If you want to export to CSV as well
write.csv(master_data, "all_kpi_summary_data.csv", row.names = FALSE)
cat("Combined data also saved to 'all_kpi_summary_data.csv'\n")