---
title: "Untitled"
author: "Zain"
date: "2025-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSe)
```

```{r}
# Load required libraries
library(dplyr)
library(tidyr)
library(openxlsx)

# Function to extract and transform data from a KPI file
process_kpi_file <- function(file_path, kpi_name) {
  # Create a temporary environment to load the data
  temp_env <- new.env()
  
  # Load the file
  load(file_path, envir = temp_env)
  
  # Get all objects in the loaded environment
  all_objects <- ls(envir = temp_env)
  
  # Initialize a list to store processed data frames
  processed_dfs <- list()
  
  # Create a log data frame to track issues
  log_df <- data.frame(
    object_name = character(),
    issue = character(),
    stringsAsFactors = FALSE
  )
  
  # Process each summary data frame
  for (obj_name in all_objects) {
    # Get the data frame
    df <- get(obj_name, envir = temp_env)
    
    # Skip if not a data frame or has no rows
    if (!is.data.frame(df) || nrow(df) == 0) {
      log_df <- rbind(log_df, data.frame(
        object_name = obj_name,
        issue = "Not a data frame or empty",
        stringsAsFactors = FALSE
      ))
      next
    }
    
    # Check if df has expected columns
    if (!all(c("Category", "Count", "Percentage") %in% names(df))) {
      log_df <- rbind(log_df, data.frame(
        object_name = obj_name,
        issue = paste("Missing columns. Available:", paste(names(df), collapse=", ")),
        stringsAsFactors = FALSE
      ))
      next
    }
    
    # Extract information from the data frame name
    name_parts <- strsplit(obj_name, "_")[[1]]
    
    # Extract market and audience
    if (length(name_parts) >= 2) {
      market <- name_parts[1]
      audience <- name_parts[2]
    } else {
      log_df <- rbind(log_df, data.frame(
        object_name = obj_name,
        issue = "Name format doesn't match expected pattern",
        stringsAsFactors = FALSE
      ))
      next
    }
    
    # Determine content_type and media_type based on the name pattern
    if (grepl("gates", obj_name)) {
      content_type <- "GF Content"
    } else {
      content_type <- "All Content"
    }
    
    # Extract media type
    if (grepl("videos", obj_name)) {
      media_type <- "Videos"
    } else if (grepl("articles", obj_name)) {
      media_type <- "Articles"
    } else if (grepl("static", obj_name)) {
      media_type <- "Static Social"
    } else {
      media_type <- "All Media"
    }
    
    # Print the unique categories for debugging
    cat("Object:", obj_name, "- Categories:", paste(unique(df$Category), collapse=", "), "\n")
    
    # Calculate the benchmark value (percentage)
    # First, determine which categories we're looking for based on the KPI
    positive_categories <- character(0)
    
    if (kpi_name == "trust") {
      positive_categories <- c("Trust", "Trusted", "Trustworthy", "1")
    } else if (kpi_name == "inspiration") {
      positive_categories <- c("Inspiration", "Inspired", "Inspiring", "1")
    } else if (kpi_name == "brand") {
      positive_categories <- c("Brand", "1")
    } else if (kpi_name == "issue") {
      positive_categories <- c("Issue", "1")
    } else if (kpi_name == "optimistic") {
      positive_categories <- c("Optimistic", "1")
    }
    
    # Look for matching categories
    benchmark <- NA
    matching_categories <- intersect(df$Category, positive_categories)
    
    if (length(matching_categories) > 0) {
      first_match <- matching_categories[1]
      row_idx <- which(df$Category == first_match)
      if (length(row_idx) > 0) {
        percentage_value <- df$Percentage[row_idx[1]]
        
        # Check if the percentage is already in decimal form (0-1) or in percentage form (0-100)
        if (!is.na(percentage_value)) {
          if (percentage_value > 100) {
            # If greater than 100, assume it needs to be divided by 100
            benchmark <- percentage_value / 100
          } else if (percentage_value <= 1) {
            # If already decimal (0-1), use as is
            benchmark <- percentage_value
          } else {
            # Otherwise assume it's a percentage (1-100) and convert to decimal
            benchmark <- percentage_value / 100
          }
        }
      }
    }
    
    # If category-based matching failed, try looking for positive patterns
    if (is.na(benchmark)) {
      # Try pattern-based matching as a fallback
      for (pattern in c("Yes", "1", "True", "Positive")) {
        row_idx <- grep(pattern, df$Category, ignore.case = TRUE)
        if (length(row_idx) > 0) {
          percentage_value <- df$Percentage[row_idx[1]]
          
          # Apply the same percentage conversion
          if (!is.na(percentage_value)) {
            if (percentage_value > 100) {
              benchmark <- percentage_value / 100
            } else if (percentage_value <= 1) {
              benchmark <- percentage_value
            } else {
              benchmark <- percentage_value / 100
            }
          }
          break
        }
      }
    }
    
    # If we still couldn't find a benchmark, look for the highest percentage
    if (is.na(benchmark) && nrow(df) > 0) {
      # Find row with maximum percentage
      max_idx <- which.max(df$Percentage)
      if (length(max_idx) > 0) {
        percentage_value <- df$Percentage[max_idx]
        cat("Using max percentage for", obj_name, ":", percentage_value, "\n")
        
        # Apply the same percentage conversion
        if (!is.na(percentage_value)) {
          if (percentage_value > 100) {
            benchmark <- percentage_value / 100
          } else if (percentage_value <= 1) {
            benchmark <- percentage_value
          } else {
            benchmark <- percentage_value / 100
          }
        }
      }
    }
    
    # Log if we couldn't determine a benchmark
    if (is.na(benchmark)) {
      log_df <- rbind(log_df, data.frame(
        object_name = obj_name,
        issue = paste("Could not determine benchmark. Categories:", 
                     paste(unique(df$Category), collapse=", ")),
        stringsAsFactors = FALSE
      ))
    }
    
    # Create a row for the benchmark table
    benchmark_row <- data.frame(
      KPI = kpi_name,
      Market = toupper(market),
      Audience = audience,
      ContentType = content_type,
      MediaType = media_type,
      Benchmark = benchmark,
      TotalCount = ifelse("TotalCount" %in% names(df), df$TotalCount[1], sum(df$Count))
    )
    
    # Add to our list
    processed_dfs[[obj_name]] <- benchmark_row
  }
  
  # Write log to file for debugging
  log_file <- paste0("log_", kpi_name, ".csv")
  if (nrow(log_df) > 0) {
    write.csv(log_df, log_file, row.names = FALSE)
    cat("Logged", nrow(log_df), "issues to", log_file, "\n")
  }
  
  # Combine all processed data frames
  if (length(processed_dfs) > 0) {
    combined_df <- bind_rows(processed_dfs)
    return(combined_df)
  } else {
    return(NULL)
  }
}

# Function to create the Excel workbook
create_benchmark_excel <- function(kpi_files, output_file = "KPI_Benchmarks.xlsx") {
  # Create a list to store data from each KPI
  all_kpi_data <- list()
  
  # Process each KPI file
  for (i in seq_along(kpi_files)) {
    file_path <- kpi_files[i]
    
    # Extract KPI name from the file path
    kpi_name <- gsub("kpi_", "", gsub(".RData", "", basename(file_path)))
    
    cat("Processing", kpi_name, "data...\n")
    
    # Process the file
    kpi_data <- process_kpi_file(file_path, kpi_name)
    
    if (!is.null(kpi_data)) {
      # Count missing values
      missing_count <- sum(is.na(kpi_data$Benchmark))
      if (missing_count > 0) {
        cat("  Warning:", missing_count, "out of", nrow(kpi_data), 
            "benchmark values are missing for", kpi_name, "\n")
      }
      
      # Check for extreme values
      if (any(kpi_data$Benchmark > 1, na.rm = TRUE)) {
        cat("  Warning: Some benchmark values are > 1 for", kpi_name, 
            "- max value:", max(kpi_data$Benchmark, na.rm = TRUE), "\n")
      }
      
      all_kpi_data[[kpi_name]] <- kpi_data
      cat("  Processed", nrow(kpi_data), "benchmark values for", kpi_name, "\n")
    } else {
      cat("  No data processed for", kpi_name, "\n")
    }
  }
  
  # Combine all KPI data
  if (length(all_kpi_data) > 0) {
    master_data <- bind_rows(all_kpi_data)
    cat("\nCombined", nrow(master_data), "total benchmark values\n")
    
    # Check for missing values in the combined data
    missing_count <- sum(is.na(master_data$Benchmark))
    if (missing_count > 0) {
      cat("Warning:", missing_count, "out of", nrow(master_data), 
          "total benchmark values are missing\n")
    }
  } else {
    stop("No data could be processed from the KPI files")
  }
  
  # Create a pivot table for each KPI
  kpi_pivot_tables <- list()
  
  for (kpi in unique(master_data$KPI)) {
    kpi_data <- master_data %>% filter(KPI == kpi)
    
    pivot_data <- kpi_data %>%
      # Create a combination column for content and media type
      mutate(ContentMedia = paste(MediaType, ContentType, sep = ", ")) %>%
      # Select only the columns we need for pivoting
      select(Market, Audience, ContentMedia, Benchmark) %>%
      # Pivot to the desired format
      pivot_wider(
        id_cols = c(Market, Audience),
        names_from = ContentMedia,
        values_from = Benchmark
      )
    
    kpi_pivot_tables[[kpi]] <- pivot_data
  }
  
  # Create a combined table with all data in a format ready for filtering
  filter_table <- master_data %>%
    select(KPI, Market, Audience, ContentType, MediaType, Benchmark)
  
  # Create the Excel workbook
  wb <- createWorkbook()
  
  # Add a main data sheet for filtering
  addWorksheet(wb, "All Benchmarks")
  writeData(wb, "All Benchmarks", filter_table, startRow = 1, startCol = 1)
  addFilter(wb, "All Benchmarks", row = 1, cols = 1:ncol(filter_table))
  
  # Format the All Benchmarks sheet
  headerStyle <- createStyle(
    textDecoration = "bold",
    halign = "center",
    fgFill = "#4F81BD",
    fontColour = "white",
    border = "bottom"
  )
  
  addStyle(wb, "All Benchmarks", headerStyle, rows = 1, cols = 1:ncol(filter_table))
  
  # Format benchmark as percentage with proper decimals
  pctStyle <- createStyle(numFmt = "0.0%")
  benchmark_col <- which(names(filter_table) == "Benchmark")
  addStyle(wb, "All Benchmarks", pctStyle, rows = 2:(nrow(filter_table)+1), 
           cols = benchmark_col, gridExpand = TRUE)
  
  # Add individual KPI sheets for the example table format
  for (kpi in names(kpi_pivot_tables)) {
    # Get the pivot table for this KPI
    pivot_data <- kpi_pivot_tables[[kpi]]
    
    # Add a worksheet
    addWorksheet(wb, kpi)
    
    # Write the data
    writeData(wb, kpi, pivot_data, startRow = 1, startCol = 1)
    
    # Add filters
    addFilter(wb, kpi, row = 1, cols = 1:2)  # Filter by Market and Audience
    
    # Format headers
    addStyle(wb, kpi, headerStyle, rows = 1, cols = 1:ncol(pivot_data))
    
    # Format all benchmark values as percentages
    for (col in 3:ncol(pivot_data)) {
      addStyle(wb, kpi, pctStyle, rows = 2:(nrow(pivot_data)+1), 
               cols = col, gridExpand = TRUE)
    }
    
    # Auto-adjust column widths
    setColWidths(wb, kpi, cols = 1:ncol(pivot_data), widths = "auto")
  }
  
  # Add an instructions sheet
  addWorksheet(wb, "Instructions")
  writeData(wb, "Instructions", data.frame(
    Instructions = c(
      "This workbook contains benchmark values for multiple KPIs across different markets, audiences, content types, and media types.",
      "",
      "There are two ways to use this workbook:",
      "",
      "1. 'All Benchmarks' tab: Use this tab to filter and sort benchmarks by any combination of KPI, Market, Audience, Content Type, and Media Type.",
      "",
      "2. Individual KPI tabs: Each KPI has its own tab with a pivot-table style layout showing benchmarks for all combinations of content and media types.",
      "",
      "Example of how to read the data:",
      "Market: US, Audience: POSAI, KPI: Trust, Content Type: GF Content, Media Type: Videos = XX% (benchmark value)",
      "",
      "You can use this to determine if content is:",
      "- Baseline: Within ±Y% of the benchmark",
      "- Overperforming: Above the benchmark by Y%",
      "- Underperforming: Below the benchmark by Y%"
    )
  ))
  
  # Set column width for instructions
  setColWidths(wb, "Instructions", cols = 1, widths = 120)
  
  # Save the workbook
  saveWorkbook(wb, output_file, overwrite = TRUE)
  cat("\nExcel workbook created:", output_file, "\n")
}

# Define the KPI files to process
kpi_files <- c(
  "summary_data/kpi_issue.RData",
  "summary_data/kpi_trust.RData",
  "summary_data/kpi_inspiration.RData",
  "summary_data/kpi_brand.RData",
  "summary_data/kpi_optimism.RData"
)

# Create the Excel workbook
create_benchmark_excel(kpi_files, "KPI_Benchmarks_Fixed.xlsx")