---
title: "kpi_trust"
author: "Zain"
date: "2025-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(here)

```

```{r}

 kpi <- read.csv(here("data", "kpi_var.csv"))
```

```{r}


create_trust_dfs <- function(data, country_code, audience_var = NULL) {

  if(is.null(audience_var)) {
    base_name <- paste0(country_code, "_genpop_trust")  # Default to genpop if no audience specified
  } else {
    base_name <- paste0(country_code, "_", audience_var, "_trust")
  }
  
 
  content_groups <- list(
    all_media = NULL,  
    videos = c("Videos"),
    articles = ("Articles"),
    static = c("Social Media")
  )

  result_dfs <- list()
  
  for (group_name in names(content_groups)) {
    content_types <- content_groups[[group_name]]
    
      
    df_name_all <- paste0(base_name, "_all_content_", group_name)
    
     
    base_filter <- data %>%
      select(trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market) %>%
      filter(market == country_code)
    
    
    if(!is.null(audience_var)) {
      # Add the audience variable to the selection
      base_filter <- data %>%
        select(trust1Q5, trust2Q6, trust3Q7, content_type, gates_compare_other, market, !!sym(audience_var)) %>%
        filter(market == country_code, !!sym(audience_var) == 1)
    }
    
  
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type %in% content_types)
      }
    } else {
    
      result_dfs[[df_name_all]] <- base_filter
    }
    

    df_name_gates <- paste0(base_name, "_gates_content_", group_name)
    base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_gates]] <- base_filter_gates
    }
  }
  
 
  return(result_dfs)
}

# Create all dataframes for each country and audience combination
countries <- c("us", "uk", "rsa", "in")
audience_vars <- c("OL", "po_base", "posai", "Base")
all_dfs <- list()

# create the genpop dataframes (no specific audience filtering)
for (country in countries) {
  country_dfs <- create_trust_dfs(kpi, country)  # No audience filter
  all_dfs <- c(all_dfs, country_dfs)
}

#  create dataframes for each specific audience type
for (country in countries) {
  for (audience in audience_vars) {
    country_audience_dfs <- create_trust_dfs(kpi, country, audience)
    all_dfs <- c(all_dfs, country_audience_dfs)
  }
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)


```

```{r}
## create function so that is answer 1 or 2 to 2 or more of questions condiered trust

# Function to add trust column to all existing data frames
add_trust_to_all_dfs <- function() {
  # Get names of all data frames in the global environment
  all_objects <- ls(envir = .GlobalEnv)
  df_names <- all_objects[sapply(all_objects, function(x) {
    obj <- get(x)
    is.data.frame(obj) && all(c("trust1Q5", "trust2Q6", "trust3Q7") %in% names(obj))
  })]
  
  # Counter for modified data frames
  count <- 0
  
  # Loop through each trust data frame and add the trust column
  for (df_name in df_names) {
    df <- get(df_name, envir = .GlobalEnv)
    
    # Calculate trust score and percentage_trust column more carefully
    df$trust_score <- rowSums(
      data.frame(
        trust1 = df$trust1Q5 %in% c(1, 2),
        trust2 = df$trust2Q6 %in% c(1, 2),
        trust3 = df$trust3Q7 %in% c(1, 2)
      ),
      na.rm = TRUE
    )
    
    df$percentage_trust <- ifelse(df$trust_score >= 2, "TRUST", "No Trust")
    
    # Update the data frame in the global environment
    assign(df_name, df, envir = .GlobalEnv)
    count <- count + 1
  }
  
  # Return the number of modified data frames
  message(paste("Trust column added to", count, "data frames"))
}

# Run the function to add trust columns to all appropriate data frames
add_trust_to_all_dfs()


```

```{r}

# Function to calculate trust percentages for all trust data frames
calculate_trust_percentages <- function() {
  # Get names of all data frames in the global environment that have percentage_trust column
  all_objects <- ls(envir = .GlobalEnv)
  df_names <- all_objects[sapply(all_objects, function(x) {
    obj <- get(x)
    is.data.frame(obj) && "percentage_trust" %in% names(obj)
  })]
  
  # Create a list to store all summary data frames
  trust_summaries <- list()
  
  # Loop through each data frame and calculate trust percentages
  for (df_name in df_names) {
    df <- get(df_name, envir = .GlobalEnv)
    
    # Skip empty data frames
    if (nrow(df) == 0) {
      next
    }
    
    # Count occurrences of each trust category
    counts <- table(df$percentage_trust)
    
    # Calculate percentages
    total <- sum(counts)
    percentages <- as.numeric(counts) / total * 100
    
    # Create a summary data frame
    summary_df <- data.frame(
      Category = names(counts),
      Count = as.numeric(counts),
      Percentage = round(percentages, 1)
    )
    
    # Add an identifier column for the original dataframe
    summary_df$Source = df_name
    
    # Store in our list with a new name
    summary_name <- paste0(df_name, "_summary")
    trust_summaries[[summary_name]] <- summary_df
  }
  
  # Return the list of summaries
  message(paste("Created", length(trust_summaries), "trust summary data frames"))
  return(trust_summaries)
}

# Run the function and assign the resulting summaries to the global environment
trust_summary_dfs <- calculate_trust_percentages()
list2env(trust_summary_dfs, envir = .GlobalEnv)