---
title: "kpi_brand"
author: "Zain"
date: "2025-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
library(here)

```

```{r}

 kpi <- read.csv(here("data", "kpi_var.csv"))
```

```{r}
create_brand_dfs <- function(data, country_code, audience_var = NULL) {
  if(is.null(audience_var)) {
    base_name <- paste0(country_code, "_genpop_brand")  # Default to genpop if no audience specified
  } else {
    base_name <- paste0(country_code, "_", audience_var, "_brand")
  }
  
  content_groups <- list(
    all_media = NULL,  # No additional filtering
    videos = c("Videos"),
    articles = "Articles",
    static = c("Social Media")
  )
  result_dfs <- list()
  
  for (group_name in names(content_groups)) {
    content_types <- content_groups[[group_name]]
    
    df_name_all <- paste0(base_name, "_all_content_", group_name)
    
    # Create base filter - fixed placement
    if(is.null(audience_var)) {
      # No audience variable filtering
      base_filter <- data %>%
        select(brand1Q10, brand2Q11, brand3Q12, content_type, gates_compare_other, market) %>%
        filter(market == country_code)
    } else {
      # With audience variable filtering
      base_filter <- data %>%
        select(brand1Q10, brand2Q11, brand3Q12, content_type, gates_compare_other, market, !!sym(audience_var)) %>%
        filter(market == country_code, !!sym(audience_var) == 1)
    }
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_all]] <- base_filter
    }
    
    df_name_gates <- paste0(base_name, "_gates_content_", group_name)
    base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_gates]] <- base_filter_gates
    }
  }
  
  return(result_dfs)
}

# Create all dataframes for each country and audience combination
countries <- c("us", "uk", "rsa", "in")
audience_vars <- c("OL", "po_base", "posai", "Base")
all_dfs <- list()

# create the genpop dataframes (no specific audience filtering)
for (country in countries) {
  country_dfs <- create_brand_dfs(kpi, country)  # No audience filter
  all_dfs <- c(all_dfs, country_dfs)
}

# create dataframes for each specific audience type
for (country in countries) {
  for (audience in audience_vars) {
    country_audience_dfs <- create_brand_dfs(kpi, country, audience)
    all_dfs <- c(all_dfs, country_audience_dfs)
  }
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)


