---
title: "Trust Index Top 3"
author: "Zain"
date: "2025-03-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(here)
library(tidyverse)
library(boot)
library(ggplot2)
library(dplyr)
```

```{r}

 kpi <- read.csv(here("data", "kpi_var.csv"))

```

```{r}

create_trust_dfs <- function(data, country_code = NULL, audience_var = NULL) {
  # Handle the base name differently for global vs country-specific
  if(is.null(country_code)) {
    if(is.null(audience_var)) {
      base_name <- "global_genpop_trust"
    } else {
      base_name <- paste0("global_", audience_var, "_trust")
    }
  } else {
    if(is.null(audience_var)) {
      base_name <- paste0(country_code, "_genpop_trust")
    } else {
      base_name <- paste0(country_code, "_", audience_var, "_trust")
    }
  }
  
  content_groups <- list(
    all_media = NULL,  # No additional filtering
    videos = c("Videos"),
    articles = "Articles",
    static = c("Social Media")
  )
  result_dfs <- list()
  
  for (group_name in names(content_groups)) {
    content_types <- content_groups[[group_name]]
    
    df_name_all <- paste0(base_name, "_all_content_", group_name)
    
    # Modified base filter to include trust variables
    if(is.null(country_code)) {
      # Global analysis - no country filter
      base_filter <- data %>%
        select(trust, content_type, gates_compare_other, market)
      
      if(!is.null(audience_var)) {
        # Add the audience variable to the selection for specific audience
        base_filter <- data %>%
          select(trust, content_type, gates_compare_other, market, !!sym(audience_var)) %>%
          filter(!!sym(audience_var) == 1)
      }
    } else {
      # Country-specific analysis
      base_filter <- data %>%
        select(trust, content_type, gates_compare_other, market) %>%
        filter(market == country_code)
      
      if(!is.null(audience_var)) {
        # Add the audience variable to the selection for specific audience
        base_filter <- data %>%
          select(trust, content_type, gates_compare_other, market, !!sym(audience_var)) %>%
          filter(market == country_code, !!sym(audience_var) == 1)
      }
    }
    
    # Save the original trust score in a new column
    base_filter <- base_filter %>%
      mutate(trust_score = trust) %>%
      mutate(trust_category = ifelse(trust >= 4, "TRUST", "Not TRUST"))
    
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_all]] <- base_filter
    }
    
    df_name_gates <- paste0(base_name, "_gates_content_", group_name)
    base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_gates]] <- base_filter_gates
    }
  }
  
  return(result_dfs)
}

# Create all dataframes for each country, global, and audience combination
countries <- c("us", "uk", "rsa", "in")
audience_vars <- c("OL", "po_base", "posai", "Base")
all_dfs <- list()

# create the global genpop dataframe (no country filter, no specific audience filtering)
global_dfs <- create_trust_dfs(kpi)  # No country filter, no audience filter
all_dfs <- c(all_dfs, global_dfs)

# create the global audience-specific dataframes
for (audience in audience_vars) {
  global_audience_dfs <- create_trust_dfs(kpi, NULL, audience)  # No country filter, specific audience
  all_dfs <- c(all_dfs, global_audience_dfs)
}

# create the country-specific genpop dataframes (no specific audience filtering)
for (country in countries) {
  country_dfs <- create_trust_dfs(kpi, country)  # Country filter, no audience filter
  all_dfs <- c(all_dfs, country_dfs)
}

# create dataframes for each specific country and audience type
for (country in countries) {
  for (audience in audience_vars) {
    country_audience_dfs <- create_trust_dfs(kpi, country, audience)
    all_dfs <- c(all_dfs, country_audience_dfs)
  }
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)

```

```{r}

# Function to calculate trust percentages with confidence intervals
calculate_trust_percentages <- function() {
  # Get all objects in global environment
  all_objects <- ls(envir = .GlobalEnv)
  
  # Create lists to store the summary dataframes
  trust_summaries <- list()
  trust_summaries_full <- list()
  
  # Count how many dataframes we process
  df_count <- 0
  
  # Process each object that is a dataframe and has a "trust_category" column
  for (obj_name in all_objects) {
    # Skip the function itself or any other non-dataframe objects
    if (obj_name == "calculate_trust_percentages") next
    
    # Try to get the object
    obj <- tryCatch({
      get(obj_name, envir = .GlobalEnv)
    }, error = function(e) {
      NULL
    })
    
    # Check if it's a dataframe with a trust_category column
    if (is.data.frame(obj) && "trust_category" %in% names(obj)) {
      df_count <- df_count + 1
      
      # Count total respondents
      total_count <- nrow(obj)
      
      # Count trust respondents (using the correct case)
      trust_count <- sum(obj$trust_category == "TRUST", na.rm = TRUE)
      
      # Calculate percentage
      trust_percentage <- (trust_count / total_count) * 100
      
      # Calculate confidence interval (Wilson score interval for proportions)
      # Using 95% confidence level (z=1.96) for 99 % CI use 2.576
      z <- 2.576
      p <- trust_count / total_count
      
      # Avoid division by zero
      if (total_count > 0) {
        # Wilson score interval formula
        # Wilson score interval formula
   denominator <- 1 + (z^2/total_count)
  center <- (p + (z^2/(2*total_count))) / denominator
  error_margin <- z * sqrt((p*(1-p)/total_count) + (z^2/(4*total_count*total_count))) / denominator
        
        ci_lower <- max(0, (center - error_margin) * 100)
        ci_upper <- min(100, (center + error_margin) * 100)
        
        # Calculate margin of error in percentage points
        margin_of_error <- error_margin * 100
      } else {
        ci_lower <- NA
        ci_upper <- NA
        margin_of_error <- NA
      }
      
      # Calculate full statistics first (we need these for calculations)
      summary_full <- data.frame(
        Category = "Trust",
        Percentage = round(trust_percentage, 0),
        CI_Lower = round(ci_lower, 0),
        CI_Upper = round(ci_upper, 0),
        Margin_of_Error = round(margin_of_error, 0),  # Margin of error rounded to nearest whole number
        Sample_Size = total_count,
        CI_Range = paste0(round(ci_lower, 0), "% - ", round(ci_upper, 0), "%"),
        MOE_Display = paste0("+/-", round(margin_of_error, 0), " pp")  # Using +/- instead of ±
      )
      
      # Create a simplified version with only the requested columns
      summary_df <- summary_full %>%
        select(Category, Percentage, MOE_Display) %>%
        mutate(Source = obj_name)  # Add the Source column
      
      # Store in our list with a new name
      summary_name <- paste0(obj_name, "_summary")
      trust_summaries[[summary_name]] <- summary_df
      
      # Also store the full data in a separate list if needed for reference
      full_name <- paste0(obj_name, "_summary_full")
      trust_summaries_full[[full_name]] <- summary_full
    }
  }
  
  # Return the list of summaries
  message(paste("Created", length(trust_summaries), "trust summary data frames"))
  
  # Return only the simplified summaries
  return(trust_summaries)
}

# EXECUTE THE FUNCTION AND STORE RESULTS
trust_summary_dfs <- calculate_trust_percentages()

# ASSIGN SUMMARIES TO GLOBAL ENVIRONMENT
list2env(trust_summary_dfs, envir = .GlobalEnv)

```

```{r}

# We'll still create the consolidated tables for reference
# Function to create a consolidated summary table
create_trust_summary_table <- function() {
  # Get all summary objects
  all_objects <- ls(pattern = "_summary$", envir = .GlobalEnv)
  
  # Create an empty dataframe to hold all summaries
  all_summaries <- data.frame()
  
  # Process each summary
  for (obj_name in all_objects) {
    # Skip if object name is our output names to avoid conflicts
    if(obj_name %in% c("all_trust_summaries", "all_trust_summaries_simple")) next
    
    # Try to get the summary dataframe
    summary_df <- tryCatch({
      get(obj_name, envir = .GlobalEnv)
    }, error = function(e) {
      NULL
    })
    
    # Only add if it's actually a dataframe
    if(is.data.frame(summary_df)) {
      # Add to the consolidated dataframe
      all_summaries <- rbind(all_summaries, summary_df)
    }
  }
  
  # Return the consolidated dataframe
  return(all_summaries)
}


# Create the consolidated summaries (but keep all individual summaries too)
all_trust_summaries <- create_trust_summary_table()
all_trust_summaries_simple <- all_trust_summaries %>%
  select(-MOE_Display)


```

```{r}

# After you've run your existing code to create trust_summary_dfs


# 2. Source the MOE functions
# (alternatively, you can copy and paste them into your script)
source("trust_moe_functions.R")

# 3. Enhance your trust summaries with MOE calculations
enhanced_summaries <- enhance_trust_summaries(
  trust_summaries = trust_summary_dfs,
  original_dfs = all_dfs,
  use_bootstrap = TRUE,  # Set to TRUE to include bootstrap CI
  conf.level = 0.99,     # 99% confidence interval
  n_boot = 1000          # Number of bootstrap samples
)

# 4. Assign enhanced summaries to global environment
list2env(enhanced_summaries, envir = .GlobalEnv)

# 5. Compare Wilson and Bootstrap MOEs
moe_comparison <- compare_moe_methods(enhanced_summaries)

# 6. View the comparison summary
head(moe_comparison)

# 7. Identify cases with very small or zero MOE
small_moe_cases <- identify_small_moe(enhanced_summaries, threshold = 0.1)

# 8. View the cases with small MOE
head(small_moe_cases)

# 9. If you want to export the results
write.csv(moe_comparison, "moe_method_comparison.csv", row.names = FALSE)
write.csv(small_moe_cases, "small_moe_cases.csv", row.names = FALSE)

```

```{r}
# Save the RData file with all summaries

save(list = ls(pattern = "_summary$"), file = "summary_data/top_3_index/kpi_trust_99_ci.RData")

```

```{r}
##bootstap ##

# Function to perform bootstrap analysis on trust data
# This assumes you already have the all_trust_summaries dataframe

# Function to perform bootstrap for a single group's data
bootstrap_trust_group <- function(group_name, original_dfs, n_boot = 1000, conf_level = 0.99) {
  # Get the original dataframe for this group (without "_summary" suffix)
  df_name <- sub("_summary$", "", group_name)
  
  # Check if the dataframe exists
  if (!df_name %in% names(original_dfs)) {
    warning(paste("Original dataframe not found for:", group_name))
    return(NULL)
  }
  
  # Get the original dataframe
  df <- original_dfs[[df_name]]
  
  # Check if trust_category exists in the dataframe
  if (!"trust_category" %in% colnames(df)) {
    warning(paste("trust_category column not found in:", df_name))
    return(NULL)
  }
  
  # Define function to calculate trust proportion
  calc_trust_prop <- function(data, indices) {
    # Sample with replacement
    boot_sample <- data[indices, ]
    
    # Calculate proportion of "TRUST" responses
    trust_prop <- mean(boot_sample$trust_category == "TRUST", na.rm = TRUE)
    
    return(trust_prop)
  }
  
  # Run bootstrap
  boot_results <- boot(data = df, statistic = calc_trust_prop, R = n_boot)
  
  # Calculate confidence interval
  alpha <- 1 - conf_level
  boot_ci <- boot.ci(boot_results, conf = conf_level, type = "perc")
  
  # Extract CI values
  ci_lower <- boot_ci$percent[4]
  ci_upper <- boot_ci$percent[5]
  
  # Calculate margin of error
  margin_of_error <- (ci_upper - ci_lower) / 2
  
  # Create result dataframe
  result <- data.frame(
    Group = group_name,
    Original_Dataframe = df_name,
    Sample_Size = nrow(df),
    Bootstrap_Iterations = n_boot,
    Trust_Proportion = boot_results$t0,
    Trust_Percentage = boot_results$t0 * 100,
    CI_Lower = ci_lower * 100,
    CI_Upper = ci_upper * 100,
    Margin_of_Error = margin_of_error * 100,
    Confidence_Level = conf_level * 100
  )
  
  return(result)
}

# Function to bootstrap all groups
bootstrap_all_trust_groups <- function(all_trust_summaries, original_dfs, n_boot = 1000, conf_level = 0.99) {
  # Get unique group names
  group_names <- unique(all_trust_summaries$Summary_Name)
  
  # Initialize list to store results
  bootstrap_results <- list()
  
  # Process each group
  for (group_name in group_names) {
    message(paste("Bootstrapping group:", group_name))
    
    result <- tryCatch({
      bootstrap_trust_group(group_name, original_dfs, n_boot, conf_level)
    }, error = function(e) {
      warning(paste("Error bootstrapping group:", group_name, "-", e$message))
      return(NULL)
    })
    
    if (!is.null(result)) {
      bootstrap_results[[group_name]] <- result
    }
  }
  
  # Combine all results into a single dataframe
  all_bootstrap_results <- do.call(rbind, bootstrap_results)
  
  return(all_bootstrap_results)
}

# Function to compare Wilson and Bootstrap margins of error
compare_wilson_bootstrap <- function(all_trust_summaries, bootstrap_results) {
  # Prepare trust summaries
  wilson_data <- all_trust_summaries %>%
    select(Summary_Name, Percentage, Margin_of_Error, Sample_Size) %>%
    rename(
      Group = Summary_Name,
      Wilson_Percentage = Percentage,
      Wilson_MOE = Margin_of_Error
    )
  
  # Prepare bootstrap data
  bootstrap_data <- bootstrap_results %>%
    select(Group, Trust_Percentage, Margin_of_Error, Sample_Size) %>%
    rename(
      Bootstrap_Percentage = Trust_Percentage,
      Bootstrap_MOE = Margin_of_Error
    )
  
  # Merge the datasets
  comparison <- merge(wilson_data, bootstrap_data, by = c("Group", "Sample_Size"))
  
  # Calculate differences
  comparison$Percentage_Diff = comparison$Bootstrap_Percentage - comparison$Wilson_Percentage
  comparison$MOE_Diff = comparison$Bootstrap_MOE - comparison$Wilson_MOE
  comparison$MOE_Ratio = comparison$Bootstrap_MOE / comparison$Wilson_MOE
  
  # Order by absolute difference in MOE
  comparison <- comparison %>%
    arrange(desc(abs(MOE_Diff)))
  
  return(comparison)
}

# Example usage:
# 1. Run bootstrap analysis on all groups
# bootstrap_results <- bootstrap_all_trust_groups(all_trust_summaries, all_dfs, n_boot = 1000, conf_level = 0.99)

# 2. Compare Wilson and Bootstrap results
# comparison <- compare_wilson_bootstrap(all_trust_summaries, bootstrap_results)

# 3. Save results
# write.csv(bootstrap_results, "bootstrap_results.csv", row.names = FALSE)
# write.csv(comparison, "wilson_bootstrap_comparison.csv", row.names = FALSE)

# 4. Identify cases with zero or very small Wilson MOE but larger bootstrap MOE
# small_wilson_moe <- comparison %>%
#   filter(Wilson_MOE < 0.5 & Bootstrap_MOE > Wilson_MOE * 2) %>%
#   arrange(desc(MOE_Ratio))

```

```{r}

# Modified bootstrap code with explicit global assignments
# Add this to the end of your script


# Run bootstrap analysis
bootstrap_results <- bootstrap_all_trust_groups(
  all_trust_summaries = all_trust_summaries, 
  original_dfs = all_dfs,
  n_boot = 100, 
  conf_level = 0.99
)

# Explicitly assign to global environment
assign("bootstrap_results", bootstrap_results, envir = .GlobalEnv)
message("Created bootstrap_results dataframe with ", nrow(bootstrap_results), " rows")

# Compare with Wilson method
comparison <- compare_wilson_bootstrap(
  all_trust_summaries = all_trust_summaries,
  bootstrap_results = bootstrap_results
)

# Explicitly assign to global environment
assign("wilson_bootstrap_comparison", comparison, envir = .GlobalEnv)
message("Created wilson_bootstrap_comparison dataframe with ", nrow(comparison), " rows")

# Find cases with small Wilson MOE but larger bootstrap MOE
small_wilson_moe <- comparison %>%
  filter(Wilson_MOE < 0.5 & Bootstrap_MOE > Wilson_MOE * 2) %>%
  arrange(desc(MOE_Ratio))

# Explicitly assign to global environment
assign("small_wilson_moe", small_wilson_moe, envir = .GlobalEnv)
message("Found ", nrow(small_wilson_moe), " cases with small Wilson MOE but larger bootstrap MOE")

# View the first few rows of the results
message("\nFirst few rows of bootstrap_results:")
print(head(bootstrap_results))

message("\nFirst few rows of wilson_bootstrap_comparison:")
print(head(wilson_bootstrap_comparison))

message("\nChecking for MOEs of exactly 0:")
zero_moe <- comparison %>% filter(Wilson_MOE == 0)
print(paste("Number of cases with Wilson MOE = 0:", nrow(zero_moe)))
if(nrow(zero_moe) > 0) {
  print(head(zero_moe))
}

```

```{r}
# Simplified bootstrap workflow specifically for your data structure


# Function to bootstrap a single trust group
bootstrap_single_group <- function(group_name, original_dfs, n_boot = 100) {
  # Get the original dataframe name (remove "_summary" suffix)
  df_name <- sub("_summary$", "", group_name)
  
  # Check if the dataframe exists
  if (!df_name %in% names(original_dfs)) {
    warning(paste("Original dataframe not found for:", group_name))
    return(NULL)
  }
  
  # Get the original dataframe
  df <- original_dfs[[df_name]]
  
  # Check if trust_category exists
  if (!"trust_category" %in% colnames(df)) {
    warning(paste("trust_category column not found in:", df_name))
    return(NULL)
  }
  
  # Define bootstrap function
  calc_trust_prop <- function(data, indices) {
    boot_sample <- data[indices, ]
    trust_prop <- mean(boot_sample$trust_category == "TRUST", na.rm = TRUE)
    return(trust_prop)
  }
  
  # Run bootstrap
  boot_results <- boot(data = df, statistic = calc_trust_prop, R = n_boot)
  
  # Calculate confidence interval
  boot_ci <- boot.ci(boot_results, conf = 0.99, type = "perc")
  
  # Extract values
  ci_lower <- boot_ci$percent[4]
  ci_upper <- boot_ci$percent[5]
  margin_of_error <- (ci_upper - ci_lower) / 2
  
  # Create result
  result <- data.frame(
    Group = group_name,
    Sample_Size = nrow(df),
    Trust_Percentage = boot_results$t0 * 100,
    CI_Lower = ci_lower * 100,
    CI_Upper = ci_upper * 100,
    Margin_of_Error = margin_of_error * 100
  )
  
  return(result)
}

# Function to run bootstrap for multiple groups with progress tracking
run_bootstrap_for_groups <- function(group_names, original_dfs, n_boot = 100) {
  results <- list()
  total_groups <- length(group_names)
  
  # Track progress
  start_time <- Sys.time()
  
  for (i in 1:length(group_names)) {
    group_name <- group_names[i]
    
    # Show progress
    message(paste0(
      "[", i, "/", total_groups, "] Processing: ", group_name,
      " (", round(i/total_groups*100), "% complete)"
    ))
    
    # Run bootstrap
    result <- tryCatch({
      bootstrap_single_group(group_name, original_dfs, n_boot)
    }, error = function(e) {
      warning(paste("Error processing", group_name, ":", e$message))
      return(NULL)
    })
    
    if (!is.null(result)) {
      results[[group_name]] <- result
    }
    
    # Save progress every 10 groups
    if (i %% 10 == 0 || i == total_groups) {
      if (length(results) > 0) {
        interim_results <- do.call(rbind, results)
        saveRDS(interim_results, "bootstrap_interim.rds")
      }
      
      # Time estimate
      current_time <- Sys.time()
      elapsed <- as.numeric(difftime(current_time, start_time, units = "mins"))
      avg_time_per_group <- elapsed / i
      remaining_groups <- total_groups - i
      est_remaining_time <- avg_time_per_group * remaining_groups
      
      message(paste(
        "Time elapsed:", round(elapsed, 1), "min.",
        "Est. remaining:", round(est_remaining_time, 1), "min."
      ))
    }
  }
  
  # Combine all results
  if (length(results) > 0) {
    all_results <- do.call(rbind, results)
    return(all_results)
  } else {
    return(NULL)
  }
}

# Main execution function
run_trust_bootstrap <- function(all_trust_summaries, all_dfs, max_groups = NULL, n_boot = 100) {
  # Get unique group names
  group_names <- unique(all_trust_summaries$Summary_Name)
  
  # Limit to subset if requested
  if (!is.null(max_groups) && max_groups < length(group_names)) {
    group_names <- group_names[1:max_groups]
    message(paste("Processing only first", max_groups, "groups"))
  }
  
  # Run bootstrap
  bootstrap_results <- run_bootstrap_for_groups(group_names, all_dfs, n_boot)
  
  # Save results
  if (!is.null(bootstrap_results)) {
    saveRDS(bootstrap_results, "bootstrap_results.rds")
    assign("bootstrap_results", bootstrap_results, envir = .GlobalEnv)
    message("Bootstrap results saved to global environment as 'bootstrap_results'")
    return(bootstrap_results)
  } else {
    message("No valid bootstrap results generated")
    return(NULL)
  }
}



test_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, max_groups = 10, n_boot = 100)


all_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, n_boot = 100)

# Comparison function for Wilson vs Bootstrap
compare_results <- function(all_trust_summaries, bootstrap_results) {
  # Extract Wilson data
  wilson_data <- all_trust_summaries %>%
    mutate(
      # Extract numeric MOE from MOE_display format ("+/-X pp")
      Wilson_MOE = as.numeric(gsub("[^0-9.]", "", MOE_Display))
    ) %>%
    select(Summary_Name, Percentage, Wilson_MOE, Sample_Size) %>%
    rename(
      Group = Summary_Name,
      Wilson_Percentage = Percentage
    )
  
  # Prepare bootstrap data
  bootstrap_data <- bootstrap_results %>%
    rename(
      Bootstrap_Percentage = Trust_Percentage,
      Bootstrap_MOE = Margin_of_Error
    )
  
  # Merge datasets
  comparison <- merge(wilson_data, bootstrap_data, by = c("Group", "Sample_Size"))
  
  # Calculate differences
  comparison$Percentage_Diff = comparison$Bootstrap_Percentage - comparison$Wilson_Percentage
  comparison$MOE_Diff = comparison$Bootstrap_MOE - comparison$Wilson_MOE
  comparison$MOE_Ratio = comparison$Bootstrap_MOE / comparison$Wilson_MOE
  
  # Sort by MOE difference
  comparison <- comparison %>%
    arrange(desc(abs(MOE_Diff)))
  
  # Save to global environment
  assign("wilson_bootstrap_comparison", comparison, envir = .GlobalEnv)
  message("Comparison saved to global environment as 'wilson_bootstrap_comparison'")
  
  return(comparison)
}





test_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, max_groups = 10, n_boot = 100)


all_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, n_boot = 100)

comparison <- compare_results(all_trust_summaries, bootstrap_results)


# Example usage:
# 1. Run bootstrap on a small subset first to test
# test_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, max_groups = 10, n_boot = 100)

# 2. If test is successful, run on all groups
 all_results <- run_trust_bootstrap(all_trust_summaries, all_dfs, n_boot = 100)

# 3. Compare with Wilson
# comparison <- compare_results(all_trust_summaries, bootstrap_results)

# 4. Find cases with small Wilson MOE but larger bootstrap MOE
# small_moe_cases <- comparison %>%
#   filter(Wilson_MOE < 1 & Bootstrap_MOE > Wilson_MOE * 2) %>%
#   arrange(desc(MOE_Ratio))



write.csv(bootstrap_results, file = "C:/Users/zaina/Documents/Focal Data/KPI Benchmark/Bootstrap/bootstrap_results.csv", row.names = FALSE)







