---
title: "kpi_trust_index_top2"
author: "Zain"
date: "2025-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo =  FALSE)
```

```{r} 

library(here)
library(tidyverse)

```

```{r}

 kpi <- read.csv(here("data", "kpi_var.csv"))

```

```{r}
create_issue_dfs <- function(data, country_code, audience_var = NULL) {
  if(is.null(audience_var)) {
    base_name <- paste0(country_code, "_genpop_issue")  # Default to genpop if no audience specified
  } else {
    base_name <- paste0(country_code, "_", audience_var, "_issue")
  }
  
  content_groups <- list(
    all_media = NULL,  # No additional filtering
    videos = c("Videos"),
    articles = "Articles",
    static = c("Social Media")
  )
  result_dfs <- list()
  
  for (group_name in names(content_groups)) {
    content_types <- content_groups[[group_name]]
    
    df_name_all <- paste0(base_name, "_all_content_", group_name)
    
    # Modified base filter to include issue variables
    base_filter <- data %>%
      select(issue, content_type, gates_compare_other, market) %>%
      filter(market == country_code)
    
    if(!is.null(audience_var)) {
      # Add the audience variable to the selection
      base_filter <- data %>%
        select(issue, content_type, gates_compare_other, market, !!sym(audience_var)) %>%
        filter(market == country_code, !!sym(audience_var) == 1)
    }
    
    # Add salience variable based on issue score
    base_filter <- base_filter %>%
      mutate(salience = ifelse(issue <= 1, "Salient", "Not Salient"))
    
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_all]] <- base_filter %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_all]] <- base_filter
    }
    
    df_name_gates <- paste0(base_name, "_gates_content_", group_name)
    base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
    
    # Apply content type filter if needed
    if (!is.null(content_types)) {
      if (length(content_types) == 1) {
        # Single value
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type == content_types)
      } else {
        # Multiple values
        result_dfs[[df_name_gates]] <- base_filter_gates %>% 
          filter(content_type %in% content_types)
      }
    } else {
      # No content type filter
      result_dfs[[df_name_gates]] <- base_filter_gates
    }
  }
  
  return(result_dfs)
}

# Create all dataframes for each country and audience combination
countries <- c("us", "uk", "rsa", "in")
audience_vars <- c("OL", "po_base", "posai", "Base")
all_dfs <- list()

# create the genpop dataframes (no specific audience filtering)
for (country in countries) {
  country_dfs <- create_issue_dfs(kpi, country)  # No audience filter
  all_dfs <- c(all_dfs, country_dfs)
}

# create dataframes for each specific audience type
for (country in countries) {
  for (audience in audience_vars) {
    country_audience_dfs <- create_issue_dfs(kpi, country, audience)
    all_dfs <- c(all_dfs, country_audience_dfs)
  }
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)

```

```{r}
calculate_salience_percentages <- function() {
  # Get all objects in global environment
  all_objects <- ls(envir = .GlobalEnv)
  
  # Create a list to store the summary dataframes
  salience_summaries <- list()
  
  # Count how many dataframes we process
  df_count <- 0
  
  # Process each object that is a dataframe and has a "salience" column
  for (obj_name in all_objects) {
    # Skip the function itself or any other non-dataframe objects
    if (obj_name == "calculate_salience_percentages") next
    
    # Try to get the object
    obj <- tryCatch({
      get(obj_name, envir = .GlobalEnv)
    }, error = function(e) {
      NULL
    })
    
    # Check if it's a dataframe with a salience column
    if (is.data.frame(obj) && "salience" %in% names(obj)) {
      df_count <- df_count + 1
      
      # Count total respondents
      total_count <- nrow(obj)
      
      # Count salient respondents
      salient_count <- sum(obj$salience == "Salient", na.rm = TRUE)
      
      # Calculate percentage
      salient_percentage <- (salient_count / total_count) * 100
      
      # Create a summary data frame with only the percentage
      summary_df <- data.frame(
        Category = "Salient",
        Percentage = round(salient_percentage, 1)
      )
      
      # Add an identifier column for the original dataframe
      summary_df$Source = obj_name
      
      # Store in our list with a new name
      summary_name <- paste0(obj_name, "_summary")
      salience_summaries[[summary_name]] <- summary_df
    }
  }
  
  # Return the list of summaries
  message(paste("Created", length(salience_summaries), "salience summary data frames"))
  return(salience_summaries)
}

# EXECUTE THE FUNCTION AND STORE RESULTS
salience_summary_dfs <- calculate_salience_percentages()

# ASSIGN SUMMARIES TO GLOBAL ENVIRONMENT
list2env(salience_summary_dfs, envir = .GlobalEnv)


```




















```{r}



# Step 1: Add the issue_category column to all data frames
add_issue_category <- function() {
  all_objects <- ls(envir = .GlobalEnv)
  df_names <- all_objects[sapply(all_objects, function(x) {
    obj <- get(x)
    is.data.frame(obj) && "issue" %in% names(obj)
  })]
  
  count <- 0
  
  # Loop through each data frame and add the issue category
  for (df_name in df_names) {
    df <- get(df_name, envir = .GlobalEnv)
    
    # Create the issue_category column based on the issue variable
    # If issue is 0 or 1, categorize as "Salient", otherwise "Not Salient"
    df$issue_category <- ifelse(df$issue %in% c(0, 1), "Salient", "Not Salient")
    
    # Update the data frame in the global environment
    assign(df_name, df, envir = .GlobalEnv)
    count <- count + 1
  }
  
  # Return the number of modified data frames
  message(paste("Issue category added to", count, "data frames"))
  return(count)
}

```



```{r}

calculate_issue_percentages <- function() {
  # Get names of all data frames in the global environment that have issue_category column
  all_objects <- ls(envir = .GlobalEnv)
  df_names <- all_objects[sapply(all_objects, function(x) {
    obj <- get(x)
    is.data.frame(obj) && "issue_category" %in% names(obj)
  })]
  
  # Create a list to store all summary data frames
  issue_summaries <- list()
  
  # Loop through each data frame and calculate salient percentages
  for (df_name in df_names) {
    df <- get(df_name, envir = .GlobalEnv)
    
    # Skip empty data frames
    if (nrow(df) == 0) {
      next
    }
    
    # Calculate percentages for salient issues only
    total <- nrow(df)
    positive_count <- sum(df$issue_category == "Salient", na.rm = TRUE)
    positive_percentage <- positive_count / total * 100
    
```
    
```{r}

    # Create a summary data frame
    summary_df <- data.frame(
      Category = "Salient",
      Count = positive_count,
      Percentage = round(positive_percentage, 1)
    )
    
    # Add an identifier column for the original dataframe
    summary_df$Source = df_name
    
    # Store in our list with a new name
    summary_name <- paste0(df_name, "_summary")
    issue_summaries[[summary_name]] <- summary_df
  }
  
  # Return the list of summaries
  message(paste("Created", length(issue_summaries), "issue summary data frames"))
  return(issue_summaries)
}

# Run the function and assign the resulting summaries to the global environment
issue_summary_dfs <- calculate_issue_percentages()
list2env(issue_summary_dfs, envir = .GlobalEnv)



