---
title: "trust_with_subject_no_content"
author: "Zain"
date: "2025-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}

library(tidyverse)
library(here)

```

```{r}
 kpi <- read.csv(here("data", "kpi_var.csv"))

```


```{r}

create_trust_dfs <- function(data, country_code, audience_var = NULL, subject) {
  # Base name construction for market and audience
  if(is.null(audience_var)) {
    base_name <- paste0(country_code, "_genpop_trust")  # Default to genpop if no audience specified
  } else {
    base_name <- paste0(country_code, "_", audience_var, "_trust")
  }
  

  base_name <- paste0(base_name, "_", subject)
  
  result_dfs <- list()
  
  df_name_all <- paste0(base_name, "_all_content")
  
  # Base filter with all relevant variables 
 
  base_cols <- c("trust", "gates_compare_other", "market", 
                "health", "science_innovation", "agriculture", "education", 
                "development_issues", "environment_climate_change", "gender.y")
  
  if(!is.null(audience_var)) {
    base_cols <- c(base_cols, audience_var)
  }
  
  # Start with base filter by country
  base_filter <- data %>%
    select(all_of(base_cols)) %>%
    filter(market == country_code)
  
  # Add audience filtering if specified
  if(!is.null(audience_var)) {
    base_filter <- base_filter %>%
      filter(!!sym(audience_var) == 1)
  }
  
  # Filter by subject or no_subject
  if(subject == "no_subject") {
    # For "no_subject", filter where ALL subject variables are 0
    subject_cols <- c("health", "science_innovation", "agriculture", "education", 
                     "development_issues", "environment_climate_change", "gender.y")
    
    # Create a filter where all subject columns equal 0
    base_filter <- base_filter %>%
      filter(health == 0 & 
             science_innovation == 0 & 
             agriculture == 0 & 
             education == 0 & 
             development_issues == 0 & 
             environment_climate_change == 0 & 
             gender.y == 0)
  } else if(subject %in% names(base_filter)) {
    # For specific subjects, filter as before
    base_filter <- base_filter %>%
      filter(!!sym(subject) == 1)
  } else {
    warning(paste("Subject column", subject, "not found in the data"))
    # Return empty list if subject not found
    return(list())
  }
  
  # Save the original trust score in a new column and categorize
  base_filter <- base_filter %>%
    mutate(trust_score = trust) %>%
    mutate(trust_category = ifelse(trust >= 5, "TRUST", "Not TRUST"))
  
  # Store the all content dataframe
  result_dfs[[df_name_all]] <- base_filter
  
  # Create gates-specific dataframe
  df_name_gates <- paste0(base_name, "_gates_content")
  base_filter_gates <- base_filter %>% filter(gates_compare_other == 1)
  
  # Store the gates content dataframe
  result_dfs[[df_name_gates]] <- base_filter_gates
  
  return(result_dfs)
}

# Define all dimensions for our analysis
countries <- c("us", "uk", "rsa", "in")
audience_vars <- c("OL", "po_base", "posai", "Base")
subjects <- c("health", "science_innovation", "agriculture", "education", 
              "development_issues", "environment_climate_change", "gender.y", "no_subject")
all_dfs <- list()

# Create data frames for all country, audience, subject combinations
for (country in countries) {
  # For genpop with each subject
  for (subject in subjects) {
    country_subject_dfs <- create_trust_dfs(kpi, country, NULL, subject)
    all_dfs <- c(all_dfs, country_subject_dfs)
  }
  
  # For each specific audience and subject combination
  for (audience in audience_vars) {
    for (subject in subjects) {
      country_audience_subject_dfs <- create_trust_dfs(kpi, country, audience, subject)
      all_dfs <- c(all_dfs, country_audience_subject_dfs)
    }
  }
}

# Assign the dataframes to the global environment
list2env(all_dfs, envir = .GlobalEnv)

```

```{r}

# Calculate trust percentages (no changes needed here)
calculate_trust_percentages <- function() {
  # Get all objects in global environment
  all_objects <- ls(envir = .GlobalEnv)
  
  # Create a list to store the summary dataframes
  trust_summaries <- list()
  
  # Count how many dataframes we process
  df_count <- 0
  
  # Process each object that is a dataframe and has a "trust_category" column
  for (obj_name in all_objects) {
    # Skip the function itself or any other non-dataframe objects
    if (obj_name == "calculate_trust_percentages") next
    
    # Try to get the object
    obj <- tryCatch({
      get(obj_name, envir = .GlobalEnv)
    }, error = function(e) {
      NULL
    })
    
    # Check if it's a dataframe with a trust_category column
    if (is.data.frame(obj) && "trust_category" %in% names(obj)) {
      df_count <- df_count + 1
      
      # Count total respondents
      total_count <- nrow(obj)
      
      # Skip data frames with zero rows
      if (total_count == 0) {
        next
      }
      
      # Count trust respondents (using the correct case)
      trust_count <- sum(obj$trust_category == "TRUST", na.rm = TRUE)
      
      # Calculate percentage
      trust_percentage <- (trust_count / total_count) * 100
      
      # Create a summary data frame with only the percentage
      summary_df <- data.frame(
        Category = "Trust",
        Percentage = round(trust_percentage, 1)
      )
      
      # Add an identifier column for the original dataframe
      summary_df$Source = obj_name
      
      # Store in our list with a new name
      summary_name <- paste0(obj_name, "_summary")
      trust_summaries[[summary_name]] <- summary_df
    }
  }
  
  # Return the list of summaries
  message(paste("Created", length(trust_summaries), "trust summary data frames"))
  return(trust_summaries)
}

# EXECUTE THE FUNCTION AND STORE RESULTS
trust_summary_dfs <- calculate_trust_percentages()

# ASSIGN SUMMARIES TO GLOBAL ENVIRONMENT
list2env(trust_summary_dfs, envir = .GlobalEnv)